Generating the Blueprints of the Java Ecosystem

### 2015-02-23 msr.tex
minor edits
added clmt publication

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics have appeared in the literature. Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools. % dimitro@bkarak: provide corresponding refs. Also you need to bulk this up. A paragraph referring to what we did. e.g "In this paper we present a dataset produced by applying three tools on all versions of a snapshot of the Maven repository. [...]".

\section{Dataset Contents}
\label{sec:data}

@@

  \item \textbf{CLMT} \textit{(clmt)} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
\end{itemize}

>>>>

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics have appeared in the literature. Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

In this paper, we present a dataset that contains popular metrics, focusing on providing calculation for a large collection of the Java ecosystem. For this purpose we selected the maven~\cite{MAVEN} repository. The tools that provided the metrics are well-known.

% dimitro@bkarak: provide corresponding refs. Also you need to bulk this up. A paragraph referring to what we did. e.g "In this paper we present a dataset produced by applying three tools on all versions of a snapshot of the Maven repository. [...]".

\section{Dataset Construction Process}
\label{sec:data}

@@

  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
\end{itemize}
